---
title: "`r paste('Experiment', ifelse(stringr::str_detect(getwd(), 'exp3'), 3, 2), 'Practice Cued Task Switching Analyses')`"
author: "Dave Braun"
date: "7/21/2019"
output: 
  html_document:
    code_folding: hide
    df_print: paged
    includes:
      after_body: ../../../../footer.html
      in_header: ../../../../favicon.html
knit:
  (function(inputFile, encoding) {
      rmarkdown::render(inputFile,
                    encoding = encoding,
                    output_file = 'index.html')})
---

*This document was last updated at `r Sys.time()`.*

This document is dedicated to analyzing the data from the practice cued task switching portion of Experiment `r ifelse(stringr::str_detect(getwd(), 'exp3'), 3, 2)`. Subjects performed 9, 17-trial cycles of cued tasks switching, for a total of 153 trials. I'm going to trim these data the same way that the perforamnce data for DST data was trimmed, and then perform two paired t-tests were transition predicts (1) RT and (2) error rate.

```{r include = FALSE}
library(tidyverse)
library(data.table)
```


```{r}
d <- read.csv('../../../data/pracCued.csv')
badSubjects <- read.csv('../../../data/badSubjects.csv')

d <- data.table(d)[!(d$subject %in% badSubjects$subject)]
N <- d %>% 
  group_by(subject) %>% 
  summarize(n()) %>% 
  nrow()
```
**The sample size is `r N`**

```{r}
initialRows <- nrow(d)
print(paste('Number of rows before trimming RTs > 10 s:', initialRows))
d <- d[d$rt < 10000]
print(paste('Number of rows after trimming RTs > 10 s:', nrow(d)))

trimmingSummary <- data.frame(Data.Dropped = round(1 - (nrow(d) / initialRows), 2), Reason = 'RTs longer than 10 s')

initialRows <- nrow(d)
d <- d %>% 
  group_by(subject) %>% 
  summarize(mRt = mean(rt), sRt = sd(rt)) %>% 
  inner_join(d, by = 'subject') %>% 
  mutate(goodTrial = ifelse(rt > mRt + 2 * sRt | rt < mRt - 2 * sRt, 0, 1)) %>% 
  filter(goodTrial == 1, transition != 'startBlock') %>% 
  select(-goodTrial, -mRt, -sRt)
print(paste('Number of rows before trimming based on +/- 2 SDs on subject-wise means:', initialRows))
print(paste('Number of rows after trimming based on +/- 2 SDs on subject-wise means:', nrow(d)))

trimmingSummary <- rbind(trimmingSummary, data.frame(Data.Dropped = round(1 - (nrow(d) / initialRows), 2), Reason = 'RTs more extreme than +/- 2 SDs beyond subject-wise means.'))
trimmingSummary
```


## Error rate analysis

```{r}
sMeans <- d %>% 
  group_by(subject, transition) %>% 
  summarize(error = mean(error))

sMeans %>% 
  group_by(transition) %>% 
  summarize(Err = mean(error), se = sd(error) / sqrt(N))

t1 <- t.test(sMeans[sMeans$transition == 'repeat',]$error, sMeans[sMeans$transition == 'switch',]$error, paired = TRUE)
t1
```

```{r}
statSum <- paste('t(', t1$parameter, ') = ', abs(round(t1$statistic,2)), ', p ', ifelse(t1$p.value < .001, '< .001', round(t1$p.value, 3)), sep = '')
sMeans %>% 
  group_by(transition) %>% 
  summarize(err = mean(error), se = sd(error) / sqrt(N)) %>% 
  ggplot(aes(x = transition, y = err)) +
  geom_bar(stat = 'identity', color = 'black') +
  geom_errorbar(aes(ymin = err - se, ymax = err + se), width = 0.5) +
  scale_x_discrete(name = 'Transition', labels = c(`repeat` = 'Repeat', `switch` = 'Switch')) +
  ylab('Error Rate')+
  annotate('text', x = 'repeat', y = .07, label = statSum) +
  theme_bw()
```



## RT analysis

```{r}
## trim errors 
initialRows <- nrow(d)
d <- d %>% 
  mutate(errorTrim = ifelse(error | shift(error), 1, 0)) %>% 
  filter(error == 0, errorTrim == 0)
print(paste('Number of rows before trimming error trials and trials following error trials:', initialRows))
print(paste('Number of rows after trimming error trials and trials following error trials:', nrow(d)))

write.csv(d, '../../../data/pracCuedClean.csv', row.names = FALSE)

trimmingSummary <- rbind(trimmingSummary, data.frame(Data.Dropped = round(1 - (nrow(d) / initialRows), 2), Reason = 'Error trials and trials following error trials'))
trimmingSummary
```

```{r}
sMeans <- d %>% 
  group_by(subject, transition) %>% 
  summarize(rt = mean(rt))

sMeans %>% 
  group_by(transition) %>% 
  summarize(Response.Time = mean(rt), se = sd(rt) / sqrt(N))

t1 <- t.test(sMeans[sMeans$transition == 'repeat',]$rt, sMeans[sMeans$transition == 'switch',]$rt, paired = TRUE)
t1
```


```{r}
statSum <- paste('t(', t1$parameter, ') = ', abs(round(t1$statistic,2)), ', p ', ifelse(t1$p.value < .001, '< .001', round(t1$p.value, 3)), sep = '')
sMeans %>% 
  group_by(transition) %>% 
  summarize(RT = mean(rt), se = sd(rt) / sqrt(N)) %>% 
  ggplot(aes(x = transition, y = RT)) +
  geom_bar(stat = 'identity', color = 'black') +
  geom_errorbar(aes(ymin = RT - se, ymax = RT + se), width = 0.5) +
  scale_x_discrete(name = 'Transition', labels = c(`repeat` = 'Repeat', `switch` = 'Switch')) +
  ylab('Response Time (ms)')+
  annotate('text', x = 'repeat', y = 1400, label = statSum) +
  theme_bw()
```




















