---
title: "Experiment 1 Moving Reference Point Analysis"
author: "Dave Braun"
date: "July 22, 2019"
output: 
  html_document:
    code_folding: hide
    df_print: paged
    includes:
      after_body: ../../../../footer.html
      in_header:after_body: ../../../../favicon.html
knit:
  (function(inputFile, encoding) {
      rmarkdown::render(inputFile,
                    encoding = encoding,
                    output_file = 'index.html')})
---

```{r include = FALSE}
library(tidyverse)
library(ez)
library(data.table)
source('../../formatSimpleEffects.r')
```

This document is dedicated to conducting the analysis to test for evidence of the reference point shifting throughout the experiment.

# Design and Predictions
**Design.** The design and analysis is a 2 (difficulty: harder than reference vs. easier than reference) X 2 (lagged difficulty: difficulty condition on previous block) within-subjects ANOVA on proportion selection of the reference deck.  
**Predictions.** If the reference point moves as a function of what condition is being performed, then there should be a simple effect of lagged difficulty within the harder-than-reference condition, where selection of reference would be greater if the previous block was a harder-than-reference block rather than if it was an easier-than-reference block.



# Results

## Response Times
Below is the cleaned data:
```{r}
d <- read.csv('../../../data/dstClean.csv')

n <- d %>% 
  group_by(subject) %>% 
  summarize(n()) %>% 
  nrow(.)

## code lagged difficulty
d <- d %>% 
  group_by(subject, block, cycle) %>% 
  summarize(difficulty = difficulty[1]) %>% 
  ungroup() %>% 
  mutate(lagDifficulty = lag(difficulty)) %>% 
  select(-difficulty) %>% 
  inner_join(d) %>% 
  mutate(trash = ifelse(block == 1 & cycle == 1, 1, 0)) %>% 
  filter(trash == 0) %>% 
  select(-trash)
d <- d %>% 
  mutate(selRefDeck = ifelse(chosenDeckId == 'reference', 1, 0))
d
```
**The sample size is `r n`.**

### Visualize the Results

```{r}
cellMeans <- d %>% 
  group_by(subject, difficulty, lagDifficulty) %>% 
  summarize(srd = mean(selRefDeck)) %>% 
  group_by(difficulty, lagDifficulty) %>% 
  summarize(selRefDeck = mean(srd), se = sd(srd) / sqrt(n()))
cellMeans
cellMeans %>% 
  ggplot(aes(x = difficulty, y = selRefDeck, group = lagDifficulty)) + 
  geom_bar(stat = 'identity', aes(fill = lagDifficulty), color = 'black', position = position_dodge(width = 0.9)) + 
  geom_errorbar(aes(ymin = selRefDeck - se, ymax = selRefDeck + se), position = position_dodge(width = 0.9), width = 0.5) + 
  theme_bw() +
  xlab('Difficulty') + 
  ylab('Proportion Selection of Reference Deck') + 
  ylim(0,1) +
  scale_fill_manual(name = 'Lagged Difficulty', values = c('Easier than Reference' = 'Light Grey', 'Harder than reference' = 'Black')) +
  theme(strip.background = element_rect(color = 'black', fill = 'white'),
        legend.position = 'top')
```


### Statistics
**Subject-wise cell means**
```{r}
d %>% 
  group_by(subject, lagDifficulty, difficulty) %>% 
  summarize(selRefDeck = mean(selRefDeck)) 
  
```

**Omnibus Model**  

**This is breaking because the factors aren't fully between or within.**  
I think I'll have to think about this one some more.

```{r}
m1 <- ezANOVA(wid = subject, between = .(difficulty, lagDifficulty), dv = selRefDeck, data = d, detailed = TRUE)
m1
cs <- c(colnames(m1$ANOVA), 'n2p')
omni <- cbind(m1, data.frame(n2p = m1$ANOVA$SSn / (m1$ANOVA$SSn + m1$ANOVA$SSd)))
colnames(omni) <- cs
omni
```

## Updated analysis (4-16)

I want to do a basic check as to whether or not the pattern of effects looks different when a condition is the first one a subject encountered vs. when it isn't


```{r}
d <- read.csv('../../../data/dstClean.csv')

d$isFirstBlock <- ifelse(d$cycle == 1 & d$block == 1, 'First Block', 'Not First Block')

d %>% 
  group_by(subject, isFirstBlock, condition) %>% 
  summarize(srd1 = mean(srd), nobs = n()) %>% 
  group_by(isFirstBlock, condition) %>% 
  summarize(srd = mean(srd1), se = sd(srd1) / sqrt(n), nobs = sum(nobs)) %>% 
  #filter(isFirstBlock == 'First Block')
  ggplot(aes(x = condition, y = srd)) + 
  geom_hline(yintercept = .5, linetype = 'dotted') +
  geom_line() + 
  geom_errorbar(aes(ymin = srd - se, ymax = srd + se)) +
  geom_point(size = 2) +
  geom_label(aes(label = nobs), nudge_y = -.10) +
  facet_wrap(~isFirstBlock) + 
  scale_x_continuous(labels = c(.1, .3, .7, .9), breaks = c(.1, .3, .7, .9)) +
  ylim(0,1) +
  labs(
    y = 'Proportion Selection of Reference Deck',
    x = 'Probability of Switching for Critical Deck',
    caption = 'Labels reflect number of observations per condition'
  ) + 
  theme_bw() + 
  theme(axis.ticks = element_blank(),
        panel.grid = element_blank(),
        strip.background = element_rect(color = 'black', fill = 'white'))
  
  

```

































