---
title: "Control Mode and Risk Preference Exp 3"
author: "Dave Braun"
date: "1/5/2022"
output: 
  html_document:
    code_folding: hide
    df_print: paged
    includes:
      after_body: ../../../../footer.html
      in_header: ../../../../favicon.html
knit:
  (function(inputFile, encoding) {
      rmarkdown::render(inputFile,
                    encoding = encoding,
                    output_file = 'index.html')})
---

*This document was last updated at `r Sys.time()`.*

This document is dedicated to investigating the hypothesis that mode of control (flexible vs. stable) might influence risk preference. In operational terms, does how many switches were performed on the previous trial influence preference for safe vs. risky deck?

```{r}
library(tidyverse)
library(data.table)
library(ez)

d <- read.csv('../../../data/dstClean.csv')

head(d)

N <- length(unique(d$subject))

```


```{r}
s <- d %>% 
  group_by(subject, choiceTrial) %>% 
  summarize(difficulty = unique(difficulty), outcomeSwitch = unique(outcomeSwitch), selectedRiskyDeck = unique(selectedRiskyDeck), condition = unique(condition)) %>% 
  mutate(outcomeSwitch = as.numeric(outcomeSwitch),
    outcome_switch_lag = ifelse(subject == shift(subject), shift(outcomeSwitch), NA)) 

s %>% 
  filter(!is.na(outcome_switch_lag)) %>% 
  mutate(ssd = 1 - selectedRiskyDeck) %>% 
  group_by(subject, difficulty, outcome_switch_lag) %>% 
  summarize(ssd_ = mean(ssd)) %>% 
  group_by(difficulty, outcome_switch_lag) %>% 
  summarize(ssd = mean(ssd_), se = sd(ssd_) / sqrt(N)) %>% 
  ggplot(aes(x = factor(outcome_switch_lag), y = ssd)) + 
  geom_hline(yintercept = .5, linetype = 'dashed') + 
  geom_bar(stat = 'identity', aes(fill = difficulty), position = position_dodge(width = .9)) + 
  geom_errorbar(aes(ymin = ssd - se, ymax = ssd + se, group = difficulty), position = position_dodge(width = .9), width = .5) + 
  ylim(0,1) + 
  labs(
    x = 'Switches Performed on Previous Trial',
    y = 'Proportion Selection of Safe Deck',
    fill = 'Direction'
  ) + 
  theme_bw() + 
  theme(legend.position = c(.2,.85))
  
ggsave('exp3_flex-risk.pdf', height = 5.5, width = 7.5)
```



```{r}
anova_data <- s %>% 
  filter(!is.na(outcome_switch_lag)) %>% 
  mutate(ssd = 1 - selectedRiskyDeck) %>% 
  group_by(subject, difficulty, outcome_switch_lag) %>% 
  summarize(ssd = mean(ssd))

anova_data %>% 
  group_by(subject) %>% 
  summarize(count = n()) %>% 
  ggplot(aes(x = count)) +
  geom_histogram()
  
  


#m1 <- ezANOVA(wid = subject, dv = ssd, within = .(difficulty, outcome_switch_lag), data = anova_data, detailed = TRUE)
```

Not enough complete cells to look at this one statistically. I can bin number of switches to try to get at it statistically.

```{r}
anova_data <- s %>% 
  mutate(condition_lag = ifelse(outcome_switch_lag < 5, 'low', ifelse(outcome_switch_lag > 10, 'high', 'medium')),
         condition_lag = factor(condition_lag, levels = c('low', 'medium', 'high')),
         ssd = 1 - selectedRiskyDeck) %>% 
  filter(!is.na(condition_lag)) %>% 
  group_by(subject, difficulty, condition_lag) %>% 
  summarize(ssd = mean(ssd)) 

anova_data$condition_lag <- factor(anova_data$condition_lag, levels = c('low', 'medium', 'high'))

anova_data %>% 
  group_by(subject) %>% 
  summarize(count = n()) %>% 
  ggplot(aes(x = count)) + 
  geom_histogram()

bad_subjects <- anova_data %>% 
  group_by(subject) %>% 
  summarize(count = n()) %>% 
  filter(count != max(count)) %>% 
  select(subject)
bad_subjects <- bad_subjects$subject

anova_data <- anova_data[!(anova_data$subject %in% bad_subjects),]

anova_data %>% 
  group_by(difficulty, condition_lag) %>% 
  summarize(ssd_ = mean(ssd), se = sd(ssd) / sqrt(N)) %>% 
  ggplot(aes(x = condition_lag, y = ssd_)) + 
  geom_hline(yintercept = .5, linetype = 'dashed') + 
  geom_bar(stat = 'identity', aes(fill = difficulty), position = position_dodge(width = .9)) + 
  geom_errorbar(aes(ymin = ssd_ - se, ymax = ssd_ + se, group = difficulty), position = position_dodge(width = .9), width = .5) + 
  ylim(0, 1) + 
  labs(
    x = 'Number of Switches Performed on Previous Trial',
    y = 'Proportion Selection of Safe Deck',
    fill = 'Difficulty',
    caption = 'The interaction is significant, p = .02'
  ) + 
  theme_bw() + 
  theme(legend.position = c(.15,.85))

  
  
```



```{r}
m1 <- ezANOVA(wid = subject, dv = ssd, within = .(difficulty, condition_lag), detailed = TRUE, data = anova_data)
m1
```




## Previous Risk Preference

Looking at the plots above, I'm wondering whether it has less to do with how many switches you just did but rather whether you were risk averse or risk seeking in the previous trial. Lagged difficulty X lagged choice X current difficulty

```{r}
s$difficulty_lag <- ifelse(s$subject == shift(s$subject), shift(s$difficulty), NA)
s$ssd <- 1 - s$selectedRiskyDeck
s$ssd_lag <- ifelse(s$subject == shift(s$subject), shift(s$ssd), NA)

s %>% 
  group_by(subject, difficulty, difficulty_lag, ssd_lag) %>% 
  summarize(ssd_ = mean(ssd)) %>% 
  group_by(difficulty, difficulty_lag, ssd_lag) %>%
  summarize(ssd = mean(ssd_), se = sd(ssd_) / sqrt(N)) %>% 
  filter(!is.na(difficulty_lag)) %>% 
  ggplot(aes(x = factor(ssd_lag), y = ssd)) + 
  geom_hline(yintercept = .5, linetype = 'dashed') + 
  geom_bar(stat = 'identity', aes(fill = difficulty), position = position_dodge(width = .9)) + 
  geom_errorbar(aes(ymin = ssd - se, ymax = ssd + se, group = difficulty), position = position_dodge(width = .9), width = .5) + 
  facet_wrap(~difficulty_lag) + 
  ylim(0,1) + 
  theme_bw()  
```

Facets are lagged difficulty. Best way so far I can interpret this is that, for those who fit the overall trend on the previous trial (ssd_lag=1 and easier than reference lag & inverse), they also conform to that trend on the current trial. This isn't so for those who didn't align on previous trial. There you're just sort of seeing a main effect of risk preference---if they selected the safe option last trial, they're most risk averse this trial and vice versa.





















