---
title: "Experiment 1 Exploratory Performance"
author: "Dave Braun"
date: "9/3/2019"
output: 
  html_document:
    code_folding: hide
    df_print: paged
    includes:
      after_body: ../../../../footer.html
      in_header: ../../../../favicon.html
knit:
  (function(inputFile, encoding) {
      rmarkdown::render(inputFile,
                    encoding = encoding,
                    output_file = 'index.html')})
---
```{r include = FALSE}
library(tidyverse)
```


*This document was last updated at `r Sys.time()`.*

This document is dedicated to analyzing the performance data from Experiment 1 using regression techniques. It's being called exploratory just because these weren't the analyses originally described in the proposal.

```{r}
d <- read.csv('../../../data/dstClean.csv')
N <- d %>% 
  group_by(subject) %>% 
  summarize(n()) %>% 
  nrow()
head(d)
```
**The sample size is `r N`.**


## Observed means

```{r}
condCodes <- data.frame(chosenDeckId = unique(d$chosenDeckId), chosenDeckIdEI = c(.1,.5,.3,.9,.7))
d <- d %>% 
  inner_join(condCodes, by = 'chosenDeckId') %>% 
  mutate(chosenDeckIdEI = factor(chosenDeckIdEI))
```

```{r}
cm <- d %>% 
  group_by(subject, chosenDeckIdEI) %>% 
  summarize(mrt = mean(cuedRt)) %>% 
  group_by(chosenDeckIdEI) %>% 
  summarize(rt = mean(mrt), se = sd(mrt) / sqrt(N)) 
  

d %>% 
  group_by(subject, chosenDeckIdEI) %>% 
  summarize(rt = mean(cuedRt)) %>% 
  ggplot(aes(x = chosenDeckIdEI, y = rt)) +
  geom_jitter(height = 0, alpha = .3, width = 0.2) + 
  geom_line(data = cm, aes(x = chosenDeckIdEI, y = rt, group = 1)) +
  geom_point(data = cm, aes(x = chosenDeckIdEI, y = rt), size = 2) +
  geom_errorbar(data = cm, aes(ymin = rt - se, ymax = rt + se), width = .5) + 
  labs(
    x = 'Chosen Deck Probability of Switching',
    y = 'Response Time (ms)'
  ) + 
  theme_bw()

```



## Build the models

```{r}
d$chosenDeckIdEI <- as.double(as.character(d$chosenDeckIdEI))

m1 <- lm(cuedRt ~ chosenDeckIdEI, data = d)
newdata <- data.frame(chosenDeckIdEI = seq(0.1,0.9, .001))
newdata$linear <- m1$coefficients[1] + m1$coefficients[2] * newdata$chosenDeckIdEI
sm <- d %>% 
  group_by(subject, chosenDeckIdEI) %>% 
  summarize(cuedRt = mean(cuedRt))
m2 <- nls(cuedRt ~ a * I(chosenDeckIdEI^b), data = d, start = list(a = 1000, b = 1), trace=T)
newdata$powerfun <- m2$m$getPars()['a'] * newdata$chosenDeckIdEI^m2$m$getPars()['b']

newdata <- newdata %>% 
  gather(model, proba, linear, powerfun)

```

```{r}
cm$chosenDeckIdEI <- as.numeric(as.character(cm$chosenDeckIdEI))
d %>% 
  group_by(subject, chosenDeckIdEI) %>% 
  summarize(rt = mean(cuedRt)) %>% 
  ggplot(aes(x = chosenDeckIdEI, y = rt)) +
  geom_jitter(height = 0, alpha = .3, width = 0.01) + 
  geom_line(data = cm, aes(x = chosenDeckIdEI, y = rt, group = 1)) +
  geom_point(data = cm, aes(x = chosenDeckIdEI, y = rt), size = 2) +
  geom_errorbar(data = cm, aes(ymin = rt - se, ymax = rt + se), width = .05) + 
  geom_line(data = newdata, aes(x = chosenDeckIdEI, y = proba, color = model, group = model), size = 1.5, linetype = 'dashed') +
  scale_x_continuous(breaks = seq(.1,.9,.2), labels = seq(.1,.9,.2)) + 
  scale_color_discrete(name = 'Model', labels = c(linear = 'Linear', powerfun = 'Power')) + 
  labs(
    x = 'Chosen Deck Probability of Switching',
    y = 'Response Time (ms)'
  ) + 
  theme_bw() + 
  theme(legend.position = c(.1,.8))
```

**Model comparison**  
Linear:
```{r}
summary(m1)
```
Power:
```{r}
summary(m2)
```


Linear model AIC: **`r format(AIC(m1), scientific = FALSE)`**  
Power model AIC: **`r format(AIC(m2), scientific = FALSE)`**
 



## Add switch cost

```{r}
d <- d[d$transition != 'startBlock',]
d$chosenDeckIdEI = d$chosenDeckIdEI - 0.5
d$transitionE <- ifelse(d$transition == 'repeat', -0.5, 0.5)
m1 <- lm(cuedRt ~ chosenDeckIdEI * transition, data = d)
summary(m1)

newdata <- expand.grid(chosenDeckIdEI = seq(.1, .9, .001), transition = c(-0.5, 0.5))
newdata$chosenDeckIdEI <- newdata$chosenDeckIdEI - 0.5
newdata$proba <- m1$coefficients[1] + m1$coefficients[2] * newdata$chosenDeckIdEI + m1$coefficients[3] * newdata$transition + m1$coefficients[4] * newdata$transition * newdata$chosenDeckIdEI
newdata$transition <- ifelse(newdata$transition == -0.5, 'repeat', 'switch')
newdata$chosenDeckIdEI <- newdata$chosenDeckIdEI + 0.5
d$chosenDeckIdEI <- d$chosenDeckIdEI + 0.5

d %>% 
  group_by(subject, chosenDeckIdEI, transition) %>% 
  summarize(rt = mean(cuedRt)) %>% 
  ggplot(aes(x = chosenDeckIdEI, y = rt, group = transition)) +
  geom_jitter(aes(color = transition), width = 0.02, height = 0, alpha = 0.3)  +
  geom_line(data = newdata, aes(x = chosenDeckIdEI, y = proba, color = transition), size = 2) + 
  scale_x_continuous(breaks = seq(.1,.9,.2), labels = seq(.1,.9,.2)) + 
  labs(
    x = 'Chosen Deck Probability of Switching',
    y = 'Response Time (ms)'
  ) + 
  scale_color_manual(name = 'Transition', labels = c(`repeat` = 'Repeat', `switch`='Switch'), values = c(`repeat` = 'blue', `switch` = 'red')) + 
  theme_bw() +
  theme(legend.position = c(.1,.8))
```


Center at easy critical deck

```{r}
d$chosenDeckIdEI_c = d$chosenDeckIdEI - 0.1
m1 <- lm(cuedRt ~ chosenDeckIdEI_c * transition, data = d)
summary(m1)
```

Center at hard critical deck

```{r}
d$chosenDeckIdEI_c = d$chosenDeckIdEI - 0.9
m1 <- lm(cuedRt ~ chosenDeckIdEI_c * transition, data = d)
summary(m1)
```

















