---
title: "Experiment 3 Exploratory Choice Analyses"
author: "Dave Braun"
date: "7/21/2019"
output: 
  html_document:
    code_folding: hide
    df_print: paged
    includes:
      after_body: ../../../../footer.html
      in_header: ../../../../favicon.html
knit:
  (function(inputFile, encoding) {
      rmarkdown::render(inputFile,
                    encoding = encoding,
                    output_file = 'index.html')})
---
```{r include = FALSE}
library(tidyverse)
library(data.table)
```


*This document was last updated at `r Sys.time()`.*

This document is dedicated to trying to get a better handle on what happened in the Experiment 3 choice data. I'm going to try to break down selections by time (ie, cycle in the experiment), because that's all I can really think of that might give some extra clarity into what happened.

```{r}
d <- read.csv('../../../data/dstCleanChoice2.csv')
N <- d %>% 
  group_by(subject) %>% 
  summarize(n()) %>% 
  nrow()
head(d)
```


```{r}
d <- d %>% 
  mutate(ssd = ifelse(selectedRiskyDeck == 1, 0, 1))
choiceGroup <- d %>% 
  group_by(subject, difficulty) %>% 
  summarize(ssd = mean(ssd)) %>% 
  spread(difficulty, ssd) %>% 
  mutate(choiceDiff = abs(`Harder than Reference` - `Easier than Reference`)) %>% 
  select(subject, choiceDiff) %>% 
  ungroup() %>% 
  summarize(choiceDiff_m = mean(choiceDiff), choiceDiff_s = sd(choiceDiff))
d <- d %>% 
  group_by(subject, difficulty) %>% 
  summarize(ssd = mean(ssd)) %>% 
  spread(difficulty, ssd) %>% 
  mutate(choiceDiff = abs(`Harder than Reference` - `Easier than Reference`)) %>% 
  #mutate(choiceGroup = ifelse(choiceDiff >= choiceGroup$choiceDiff_m + choiceGroup$choiceDiff_s, 'highBias', 'lowBias')) %>% 
  mutate(choiceGroup = ifelse(choiceDiff >= .3, 'highBias', 'lowBias')) %>% 
  select(subject, choiceGroup) %>% 
  inner_join(d, by = 'subject')

d$cycleCount <- cut(d$choiceTrial, seq(0,40,10))

d %>% 
  group_by(subject, cycleCount, choiceGroup, difficulty) %>% 
  summarize(ssd = mean(ssd)) %>% 
  ggplot(aes(x = cycleCount, y = ssd, group = subject)) + 
  geom_line(alpha = .3) +
  facet_grid(choiceGroup ~ difficulty) + 
  scale_x_discrete(labels = c('1-10', '11-20', '21-30', '31-40')) + 
  labs(
    x = 'Choice Trial',
    y = 'Proportion Selection of Safe Deck'
  ) + 
  theme_bw() + 
  theme(legend.position = 'none',
        strip.background = element_rect(fill = 'white', color = 'black')) 
```


I don't think there's much to see here. Seems as though selection strategy didn't change much over the course of the experiment.

















