---
title: "Cross Experiment Rapid Fire Analyses"
author: "Dave Braun"
date: "5/18/2022"
output: 
  html_document:
    code_folding: hide
    df_print: paged

knit:
  (function(inputFile, encoding) {
      rmarkdown::render(inputFile,
                    encoding = encoding,
                    output_file = 'index.html')})
---
```{r include=FALSE}
library(tidyverse)
library(ez)
library(data.table)

e2adst <- read.csv('../exp3/data/dstCleanChoice1.csv')
e2bdst <- read.csv('../exp3-pypool/data/dstCleanChoice1.csv')
e2arf <- read.csv('../exp3/data/rapidFire.csv')
e2brf <- read.csv('../exp3-pypool/data/rapidFire.csv')

e2bdst <- e2bdst[e2bdst$corrected_effort_units == 'false',]
e2brf <- e2brf[e2brf$corrected_effort_units == 'false',]
```

This document explores the rapid fire data across Experiments 2A and 2B. 

I will trim the data separately for E2A and E2B according to:  
* Drop subjects who have average choice RTs < 200 ms  
* Drop subjects who are beyond +2 SDs on group means of location bias


```{r}
## drop for choice rts
e2abadsubjects <- e2arf %>% 
  group_by(subject) %>% 
  summarize(choiceRt = mean(choiceRt)) %>% 
  filter(choiceRt < 200)

e2bbadsubjects <- e2brf %>% 
  group_by(subject) %>% 
  summarize(choiceRt = mean(choiceRt)) %>% 
  filter(choiceRt < 200)

e2arf <- e2arf[!e2arf$subject %in% e2abadsubjects,]
e2brf <- e2brf[!e2brf$subject %in% e2abadsubjects,]
```

For trimming people who selected decks on average in less than 200 ms, there were `r nrow(e2abadsubjects)` in E2A and `r nrow(e2bbadsubjects)` in E2B.

```{r}
## drop for location bias

e2arf$experiment <- 'e2a'
e2brf$experiment <- 'e2b'
keep <- c('subject', 'experiment', 'selectedDeckLocation')
rf <- rbind(e2arf[,keep], e2brf[,keep])

p_data <- rf %>% 
  mutate(location_numeric = ifelse(selectedDeckLocation == 'left', -1, 1)) %>% 
  group_by(subject, experiment) %>% 
  summarize(location_numeric = abs(mean(location_numeric)))

means <- p_data %>% 
  group_by(experiment) %>% 
  summarize(m = mean(location_numeric), std = sd(location_numeric)) %>% 
  mutate(threshold = m + 2*std) %>% 
  select(-m, -std)

p_data %>% 
  ggplot(aes(x = reorder(subject, location_numeric), y = location_numeric)) +
  geom_point() + 
  labs(
    x = 'Subject',
    y = 'Location Bias'
  ) +
  coord_flip() + 
  facet_wrap(~experiment) + 
  geom_hline(data = means, aes(yintercept = threshold), linetype = 'dashed') +
  theme_bw() + 
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        strip.background = element_rect(color = 'black', fill = 'white')) 
  
  
```


```{r}
bad_subjects <- p_data %>% 
  inner_join(means) %>% 
  filter(location_numeric > threshold) %>% 
  select(subject, experiment)
bad_subjects

e2arf <- e2arf[!e2arf$subject %in% bad_subjects[bad_subjects$experiment=='e2a',]$subject,]
e2brf <- e2brf[!e2brf$subject %in% bad_subjects[bad_subjects$experiment=='e2b',]$subject,]
```

For location bias, there were `r nrow(bad_subjects[bad_subjects$experiment == 'e2a',])` subjects beyond the +2 SD threshold in E2A, and there were `r nrow(bad_subjects[bad_subjects$experiment == 'e2b',])` such subjects in E2B.

This left `r length(unique(e2arf$subject))` subjects in E2A, and `r length(unique(e2brf$subject))` subjects in E2B.

## Statistical tests

```{r}
## unconditional risk preference means 
e2adst <- e2adst %>% 
  group_by(subject) %>% 
  summarize(ssd = 1 - mean(selectedRiskyDeck)) %>% 
  filter(subject %in% e2arf$subject)

e2bdst <- e2bdst %>% 
  group_by(subject) %>% 
  summarize(ssd = 1 - mean(selectedRiskyDeck)) %>% 
  filter(subject %in% e2brf$subject)


## t tests on rf data

e2arfmeans <- e2arf %>% 
  group_by(subject, difficulty) %>% 
  summarize(ssd = 1 - mean(selectedRiskyDeck))

print('E2A RF means')

e2arfmeans %>% 
  group_by(difficulty) %>% 
  summarize(mean_ssd = mean(ssd), se = sd(ssd) / sqrt(nrow(e2arfmeans)))

print('E2A RF ttest')

v1 <- e2arfmeans[e2arfmeans$difficulty=='Easier than Reference',]$ssd
v2 <- e2arfmeans[e2arfmeans$difficulty=='Harder than Reference',]$ssd
t.test(v1, v2, paired = TRUE)

e2brfmeans <- e2brf %>% 
  group_by(subject, difficulty) %>% 
  summarize(ssd = 1 - mean(selectedRiskyDeck))

print('E2B RF means')

e2brfmeans %>% 
  group_by(difficulty) %>% 
  summarize(mean_ssd = mean(ssd), se = sd(ssd) / sqrt(nrow(e2arfmeans)))

print('E2B RF ttest')

v1 <- e2brfmeans[e2brfmeans$difficulty=='Easier than Reference',]$ssd
v2 <- e2brfmeans[e2brfmeans$difficulty=='Harder than Reference',]$ssd
t.test(v1, v2, paired = TRUE)


```


```{r}
## correlations
e2a <- e2arfmeans %>% 
  inner_join(e2adst, by = 'subject')
cor.test(e2a$ssd.x, e2a$ssd.y)

e2b <- e2brfmeans %>% 
  inner_join(e2bdst, by = 'subject')
cor.test(e2b$ssd.x, e2b$ssd.y)
```
























