---
title: "Experiment 2 Bayesian Analysis"
author: "Dave Braun"
date: "8/16/2019"
output: 
  html_document:
    code_folding: hide
    df_print: paged
    includes:
      after_body: ../../../../footer.html
      in_header: ../../../../favicon.html
knit:
  (function(inputFile, encoding) {
      rmarkdown::render(inputFile,
                    encoding = encoding,
                    output_file = 'index.html')})
---
```{r include = FALSE}
library(tidyverse)
library(BayesFactor)
```


*This document was last updated at `r Sys.time()`.*

This document is dedicated to investigating the null choice effects in Experiment 2 with Bayesian statistics.


```{r}
d <- read.csv('../../../data/dstCleanChoice2.csv')
head(d)
```


```{r}
scm <- d %>% 
  mutate(ssd = ifelse(selectedRiskyDeck == 1, 0, 1)) %>% 
  group_by(subject, difference, difficulty) %>% 
  summarize(ssd = mean(ssd))

smm <- d %>% 
  mutate(ssd = ifelse(selectedRiskyDeck == 1, 0, 1)) %>% 
  group_by(subject, difficulty) %>% 
  summarize(ssd = mean(ssd))
```

## Main effect of difficulty

### Frequentist

**Easier than reference**

```{r}
t.test(smm[smm$difficulty == 'Easier than Reference',]$ssd, mu = .5)
```

**Harder than reference**
```{r}
t.test(smm[smm$difficulty == 'Harder than Reference',]$ssd, mu = .5)
```


### Bayesian

**Easier than reference**

```{r}
b1 <- ttestBF(smm[smm$difficulty == 'Easier than Reference',]$ssd, mu = .5)
b1
1 / (exp(b1@bayesFactor$bf))
```

**Harder than reference**

```{r}
b2 <- ttestBF(smm[smm$difficulty == 'Harder than Reference',]$ssd, mu = .5)
b2
1 / (exp(b2@bayesFactor$bf))
```

## Simple effect of difficulty

### Frequentist 

**Easier than reference**

```{r}
scm <- scm %>% 
  filter(difference == 'Extreme')

t.test(scm[scm$difficulty == 'Easier than Reference',]$ssd, mu = .5)
```

**Harder than refernece**

```{r}
t.test(scm[scm$difficulty == 'Harder than Reference',]$ssd, mu = .5)
```


### Bayesian

**Easier than reference**

```{r}
b1 <- ttestBF(scm[scm$difficulty == 'Easier than Reference',]$ssd, mu = .5)
b1
1 / (exp(b1@bayesFactor$bf))
```

**Harder than reference**

```{r}
b2 <- ttestBF(scm[scm$difficulty == 'Harder than Reference',]$ssd, mu = .5)
b2
1 / (exp(b2@bayesFactor$bf))
```






















